Concurrent, Parallel Garbage Collection in Linear Time

### 2016-06-03 finaletd/acknowledge.tex
Thesis sections and chapters added with some clear sections to fill
done

I am very grateful to my supervisor Dr. Steven R. Brandt for giving the opportunity to fulfill my dream of pursuing Ph.D in computer science. His advice, ideas and feedback helped me understand various concepts and get better as a student. Without his continuous support and guidance, I wouldn't have come so far in my studies and research. Our almost everyday discussions were very effective and motivating.

I would also like to express my sincere gratitude to 
Dr. Costas Busch. His expertise in the area, insights,
and advices helped me to be a better researcher. Apart
from being part of my thesis committee, Dr. Gerald Baumgartner has always advised in various facets of
my graduate school life, helped me to direct my research
in broad view.

I would also like to thank Dr. Gokarna Sharma for useful feedbacks, constant help and collaborations. I would like to thank my parents for their constant moral support. It is of my pleasure to thank my sister Usha who at very early age taught me more about computers. I would also like to thank my friend Sudip Biswas, who motivated me when required and helped me to focus on my graduate school at all times.

>>>>

I am very grateful to my supervisor Dr. Steven R. Brandt for giving the opportunity to fulfill my dream of pursuing Ph.D in computer science. His advice, ideas and feedback helped me understand various concepts and get better as a student. Without his continuous support and guidance, I wouldn't have come so far in my studies and research. Our discussions were very effective and motivating.

I would also like to express my sincere gratitude to 
Dr. Costas Busch. His expertise in the area, insights, motivation to direct the research in theoretical way,
and advices helped me to be a better researcher. I would like to thank Dr. Gerald Baumgartner for his constructive feedbacks, advices, and interesting conversations about my work.

I would also like to thank Dr. Gokarna Sharma for useful feedbacks, constant help and collaborations. I would like to thank my family for their constant moral support. It is  my pleasure to thank my cousin Usha who introduced me to computers and taught me more about very early age. I would also like to thank my friends Sudip Biswas and Dennis Castleberry, who motivated me when required and helped me to focus on my graduate school at all times.
